Hippocampal replay of experience at slow speeds

### 2021-04-28 Article.tex
Update on Overleaf.

@@

We hypothesize that this large set of events supports the ability to rapidly retrieve representations of individual places and snippets of experience. Previous findings demonstrated that SWRs with movement- or immobility-related activity engage specific patterns of spiking activity outside the hippocampus \citep{YuDistincthippocampalcorticalmemory2017, JadhavCoordinatedExcitationInhibition2016}. Thus, we would expect that the large set of events with slow dynamics would also engage specific patterns of activity outside the hippocampus, perhaps allowing animals to recall and evaluate the value of specific locations or short movement trajectories without having to generate full trajectories \citep{YuHippocampalcorticalinteraction2015}.

One possibility is that these events are supported by different subcircuits within the hippocampus. For example, \cite{OlivaRoleHippocampalCA22016} showed that CA2 neurons tend to lead CA1 and CA3 neurons during SWRs We did not have enough simultaneously recorded tetrodes in each area to attribute the different dynamics to particular subregions.

>>>>

Finally, one important question is how our method compares to the standard decoder. We would like to emphasize, as we have stated in the introduction, that this comparison is complicated due to the variety of parameters and inference methods used and referred to as the standard "Bayesian" decoder.

@@

We hypothesize that this large set of events supports the ability to rapidly retrieve representations of individual places and snippets of experience. Previous findings demonstrated that SWRs with movement- or immobility-related activity engage specific patterns of spiking activity outside the hippocampus \citep{YuDistincthippocampalcorticalmemory2017, JadhavCoordinatedExcitationInhibition2016}. Thus, we would expect that the large set of events with slow dynamics would also engage specific patterns of activity outside the hippocampus, perhaps allowing animals to store and evaluate the value of specific locations or short movement trajectories without having to generate full trajectories \citep{YuHippocampalcorticalinteraction2015}.

One possibility is that these events are supported by different subcircuits within the hippocampus.For example, \cite{OlivaRoleHippocampalCA22016} showed that CA2 neurons tend to lead CA1 and CA3 neurons during SWRs. We did not have enough simultaneously recorded tetrodes in each area to attribute the different dynamics to particular subregions.
